---
title: "Sampling Lynching Coverage"
author: "(redacted - peer review)"
date: "2024-6-19"
output:
  word_document: default
  pdf_document: default
---

# Sample of Lynching Coverage

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
#install.packages("sampler")
library(sampler)
#install.packages("rio")
library(rio)
#install.packages("kableExtra")
#install.packages("formattable")
library(formattable)
library(kableExtra)
library(knitr)
library(here)
#install.packages('htmlTable')
library(htmlTable)
#install.packages("rempsyc")
library(rempsyc)
here::here('/Users/robwells/Code/lynching_press')
```

Next, we import an index of lynching coverage -- 60,042 pages -- captured by these search terms.

# Import Data
```{r}

#60,000 Library of Congress articles on lynching captured.
index <- read_csv("https://osf.io/download/hda4v/?view_only=6c106acd6cb54f6f849e8c6f9098809f")

#metadata for 11,396 articles observed by coding team. 19% of all 60,042 entries in search
master_article_index_june_26_2024 <- read_csv("https://osf.io/download/fuh3m/?view_only=6c106acd6cb54f6f849e8c6f9098809f") %>% 
  as.data.frame()

# 1650 articles from the black press
# from master_article_index_6_17 has 11,223 articles
black_press_master_june_26_2024 <- read_csv("#https://osf.io/download/e84j3/?view_only=6c106acd6cb54f6f849e8c6f9098809f")
```

Index of all Chronicling America coverage.

```{r}
#1789-1963, 18.1 million rows, all Chroniciling America as of 6/2023

#Due to the file size (1.7gb), you will need to download this file to your hard drive and import it in R from your local machine: https://osf.io/download/3kpqa/?view_only=6c106acd6cb54f6f849e8c6f9098809f


index_chron <- rio::import("/Users/YOUR_USER_NAME_HERE/Downloads/chron_am_manifest.csv")

index_chron <- janitor::clean_names(index_chron)

```


## Count years for entries 
```{r}
#Count years for Chroniciling America 
chron_count <- index_chron %>% 
count(year) %>% 
  mutate(pct = formattable::percent(n/(sum(n)))) %>% 
  rename(chron_all = n, chron_pct = pct)

#write.csv(chron_count, "../output_images_tables/chronicle_count.csv")

#Count years for all lynching articles captured
lynch_count <- index %>% 
  count(year) %>% 
  mutate(pct = formattable::percent(n/(sum(n)))) %>% 
  rename(lynch_news = n, lynch_pct = pct)

combolynch_chron <- chron_count %>% 
  inner_join(lynch_count, by="year")


```


## Viz total and lynch papers
```{r}

#Comparing total page count to the pages with lynching news

ggplot(combolynch_chron, aes(x=year)) +
  geom_line(aes(y= chron_pct), size=2, color = "red") +
  geom_line(aes(y=(lynch_pct)), size=1, color = "blue") +
  scale_y_continuous(
    name = "All Chroniciling America (Red)",
    sec.axis = sec_axis(~.*1, name="Lynching News in Chron America (Blue)")
  ) +
  scale_x_continuous(labels = c(seq(1790, 1960, 10)), breaks = seq(1790, 1960, 10)) +
  labs(title = "Lynching News to Overall News Coverage, 1789-1963",
       caption= "Comparing All Chron America to Lynching News in Chron America as Pct of All Coverage.
       Graphic by (redacted - peer review)",
       x = "Year")

```

### Comparing the 60,000 search to extracted articles
## Count years for entries 
```{r}
#Count years for extracted articles
article_count <- master_article_index_june_26_2024 %>% 
count(year) %>% 
  mutate(pct = formattable::percent(n/(sum(n)))) %>% 
  rename(article_all = n, article_pct = pct)

#write.csv(chron_count, "../output_images_tables/chronicle_count.csv")

#Count years for all lynching articles captured
lynch_count <- index %>% 
  count(year) %>% 
  mutate(pct = formattable::percent(n/(sum(n)))) %>% 
  rename(loc_count = n, loc_pct = pct)

combo_2_lynch_chron <- article_count %>% 
  inner_join(lynch_count, by="year")


```


## Viz total and lynch papers
```{r}

#Comparing total page count to the pages with lynching news

ggplot(combo_2_lynch_chron, aes(x=year)) +
  geom_line(aes(y= article_pct), size=2, color = "red") +
  geom_line(aes(y=(loc_pct)), size=1, color = "blue") +
  scale_y_continuous(
    name = "Extracted Articles (11,223 articles in LOC) (Red)",
    sec.axis = sec_axis(~.*1, name="Search Results Chron America (Blue)")
  ) +
  scale_x_continuous(labels = c(seq(1805, 1960, 10)), breaks = seq(1805, 1960, 10)) +
  labs(title = "Extracted Article Sample to Total Search Results, 1805-1963",
       caption= "Red line is the 19% of lynching articles actually extracted. The blue line is total search for lynching in Chronicling America.
       Graphic by (redacted - peer review). June 23, 2024",
       x = "Year")

```






# Tolnay Beck Bailey Victim Data - Compare Trends with News Coverage

The University of Illinois holds the Tolnay_Bailey_Victim_Data of all known lynching cases from 1882-1929.

\#<https://uofi.app.box.com/s/ffmqd2rjxrdt1tvxl38d/file/110041209555>

There are 2,249 lynching cases in this database, again from 1882-1929

There is also the Tolnay, Beck & Bailey list of 5,872 cases, 1865-2020, probable and confirmed lynchings.
https://app.box.com/s/99ggc6epn4rdvritke0h/file/992017683748


**Below, we compare the frequency of news coverage to the Tolnay victims list.**

```{r}

# This contains tolnay_beck	5871 confirmed and probable	lynchings
tolnay_beck <- read_csv("https://osf.io/download/vb8wa/?view_only=6c106acd6cb54f6f849e8c6f9098809f") %>% 
  as.data.frame()

tolnay_beck <- janitor::clean_names(tolnay_beck)


```

```{r}
#Cleaning the types of lynchings
tolnay_beck <- tolnay_beck %>% 
  mutate(
    status_clean = str_to_lower(status)) 
  

tolnay_beck$status_clean <- stringr::str_trim(tolnay_beck$status_clean)

tolnay_beck %>% 
  count(status_clean) 
```


```{r}
tolnay_events <- tolnay_beck %>% 
  select(year, status_clean) %>% 
group_by(year) %>% 
  count(status_clean)

tolnay_events %>% 
  pivot_wider(names_from = status_clean, values_from = n)



```


```{r}
tolnay_beck %>% 
count(year) %>% 
   group_by(year) %>% 
#Sandwich it onto a simple ggplot
  ggplot(aes(x = year, y = n, fill = n)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
  labs(title = "Actual, Threatened Lynchings, 1865-2020", 
       subtitle = "Count of Actual, Probable Lynchings. Tolnay-Beck Data",
       caption = "n=5,871 incidents (lynchings = 5,039. Graphic by (redacted - peer review), 4/14/2023",
       y="Count",
       x="Year")
#Actual, Threatened Lynchings Tolnay 4_14_2023
```


