---
title: "team one mob charts j389l"
author: "Khushboo Rathore"
date: "2023-09-20"
output: html_document
---

```{r}
#install.packages("here")
here::here()
library(tidyverse)
library(tidyr)
#install.packages("ggmap")
library(ggmap)
#register_google(key = "YOUR KEY HERE")
library(googlesheets4)
#install.packages("geosphere")
library(geosphere)
#install.packages("tigris")
#install.packages("zoo")
library(tigris)
library(stringr)
library(janitor)
library(zoo)
library(lubridate)

```


# FINAL PROJECT MOB ANALYSIS


### Figure 10: Mob coverage, characterization by decade Analyzing by Decade
### Figure 12: Newspaper, lynch mobs and justice narrative. 
```{r}
# install.packages("readxl")
library(readxl)

# URL to download the Excel file
excel_url <- "https://osf.io/download/zu4hk/?view_only=6c106acd6cb54f6f849e8c6f9098809f"

# File path where you want to save the downloaded Excel file
downloaded_file <- "all_mob_connected.xlsx"

# Download the Excel file to your local machine
download.file(url = excel_url, destfile = downloaded_file, mode = "wb")

# Read the Excel file into a dataframe
all_mob_connected <- read_excel(downloaded_file, sheet = "all_mob_connected")

# all_mob_connected <- read_sheet("https://docs.google.com/spreadsheets/d/1XG2um-mkZ0ta6kikMuQucydNOPV2POrWLPtxRTuBh0o/edit#gid=0", sheet = "all_mob_connected")


decade_trends <- all_mob_connected %>% 
  filter(!is.na(decade)) %>% 
  group_by(decade) %>% 
  summarize(
    hostile = sum(hostile),
    orderly = sum(orderly),
    neutral = sum(neutral),
    justice = sum(justice),
    identified = sum(identified),
    total = n(),
    percent_hostile = round(hostile/total*100,2),
    percent_orderly = round(orderly/total*100,2),
    percent_neutral = round(neutral/total*100,2),
    percent_justice = round(justice/total*100,2),
    percent_identified = round(identified/total*100,2)
  )

write_csv(decade_trends, "../output_images_tables/mob_decade_trends.csv")

```


Click here for interactive version. https://datawrapper.dwcdn.net/fm9BS/7/
Kushboo graphic.
https://datawrapper.dwcdn.net/fm9BS/7/
https://docs.google.com/spreadsheets/d/1v6uE0owA1DLjOxOVlRs4ijFleYtH87Y-VrDOGPqNOps/edit#gid=157809296
https://docs.google.com/document/d/1QrW9yvVlTMphAVpUwk3Glh5izoaY2Q5GthwjsRcG6m4/edit


## Analyzing by Region
### Figure 13: Regional trends lynching and justice. 
```{r}
regional_trends <- all_mob_connected %>% 
  filter(!is.na(newspaper_region)) %>% 
  group_by(newspaper_region) %>% 
  summarize(
    hostile = sum(hostile),
    orderly = sum(orderly),
    neutral = sum(neutral),
    justice = sum(justice),
    identified = sum(identified),
    total = n(),
    percent_hostile = round(hostile/total*100,2),
    percent_orderly = round(orderly/total*100,2),
    percent_neutral = round(neutral/total*100,2),
    percent_justice = round(justice/total*100,2),
    percent_identified = round(identified/total*100,2)
  )

write_csv(regional_trends, "../output_images_tables/mob_regional_trends.csv")
```
#Figure 12: Newspaper, lynch mobs and justice narrative. Click here for interactive version. https://datawrapper.dwcdn.net/5zp1f/3/
https://docs.google.com/spreadsheets/d/1v6uE0owA1DLjOxOVlRs4ijFleYtH87Y-VrDOGPqNOps/edit#gid=157809296
decade_percents_Justice
https://docs.google.com/document/d/1QrW9yvVlTMphAVpUwk3Glh5izoaY2Q5GthwjsRcG6m4/edit

#Figure 13: 'Lynching as justice' least likely in Northeast newspapers.
https://datawrapper.dwcdn.net/GJ6s9/4/
https://docs.google.com/spreadsheets/d/1v6uE0owA1DLjOxOVlRs4ijFleYtH87Y-VrDOGPqNOps/edit#gid=157809296
https://docs.google.com/document/d/1QrW9yvVlTMphAVpUwk3Glh5izoaY2Q5GthwjsRcG6m4/edit


## Analyzing by State
```{r}
state_trends <- all_mob_connected %>% 
  filter(!is.na(newspaper_state_clean)) %>% 
  group_by(newspaper_state_clean) %>% 
  summarize(
    hostile = sum(hostile),
    orderly = sum(orderly),
    neutral = sum(neutral),
    justice = sum(justice),
    identified = sum(identified),
    total = n(),
    percent_hostile = round(hostile/total*100,2),
    percent_orderly = round(orderly/total*100,2),
    percent_neutral = round(neutral/total*100,2),
    percent_justice = round(justice/total*100,2),
    percent_identified = round(identified/total*100,2)
  )
  
write_sheet(state_trends, "https://docs.google.com/spreadsheets/d/1XG2um-mkZ0ta6kikMuQucydNOPV2POrWLPtxRTuBh0o/edit#gid=0", sheet = "state_trends")
```

## Co-Occurences of Hostile, Justice and Orderly
```{r}
all_occurrences <- nrow(all_mob_connected)

cooccurrence_table <- all_mob_connected %>% 
  group_by(hostile, justice, orderly, neutral) %>% 
  count() %>% 
  mutate(named = case_when(
    hostile == 1 & justice == 1 & orderly == 1 & neutral == 1 ~ "all",
    hostile == 1 & justice == 1 & orderly == 1 ~ "hostile, justice, orderly",
    hostile == 1 & orderly == 1 & neutral == 1 ~ "hostile, orderly, neutral",
    orderly == 1 & justice == 1 & neutral == 1 ~ "oderly, justice, neutral",
    hostile == 1 & justice == 1 & neutral == 1 ~ "hostile, justice, neutral",
    justice == 1 & neutral == 1 ~ "justice, neutral",
    orderly == 1 & neutral == 1 ~ "orderly, neutral",
    justice == 1 & orderly == 1 ~ "justice, orderly",
    justice == 1 & hostile == 1 ~ "justice, hostile",
    orderly == 1 & hostile == 1 ~ "orderly, hostile",
    hostile == 1 & neutral == 1 ~ "hostile, neutral",
    orderly == 0 & justice == 0 & hostile == 0 & neutral == 0 ~ "none"
  )) %>% 
  filter(!is.na(named)) %>% 
  ungroup() %>% 
  select(named, n) %>% 
  mutate(percent_occurrences = round(n/all_occurrences*100,2))

write_sheet(cooccurrence_table, "https://docs.google.com/spreadsheets/d/1XG2um-mkZ0ta6kikMuQucydNOPV2POrWLPtxRTuBh0o/edit#gid=0", sheet = "co_occurrences")

```


