---
title: "Indexes and Lists"
author: "Wells"
date: "2024-04-18"
output: html_document
---


```{r}
#install.packages("here")
here::here()
library(tidyverse)
library(tidyr)
#install.packages("ggmap")
library(ggmap)
#register_google(key = "YOUR KEY HERE")
library(googlesheets4)
#install.packages("geosphere")
library(geosphere)
#install.packages("tigris")
#install.packages("zoo")
library(tigris)
library(stringr)
library(janitor)
library(zoo)
library(lubridate)
library(readtext)

```
#Data Cleaning and Compiling
April 18 data cleaning and compiling
master_article_index_4_18 has 12,579 articles
#TODO 
#--have not added the Black press articles to it yet
--add 714 articles from proquest and howard university
#TODO--331 of the LOC articles are from the black press
#TODO--total 1,045 articles from the black press
```{r}
master_article_index_4_18 <- read_csv("../data/master_article_index_4_18.csv") %>% 
  clean_names() %>% 
  mutate(date = as_date(paste(year,month,day, sep ="/"))) %>% 
   mutate(file_id2 = (paste(file_id, article_id, sep = '_')))
```



```{r}
#Add 1803 black press articles ( 714 bp articles + 1,089 LOC articles)
blackindex_master <- read.csv("../data/blackindex_master.csv")

#13,311 articles
master_article_index_4_20 <- master_article_index_4_18 %>% 
  full_join(blackindex_master, by=c("file_id2"="file_name", "newspaper_name", "newspaper_state", "date", "year", "url", "sn", "file_id", "article_id", "page", "edition", "month", "day", "mod_id"))

write.csv(master_article_index_4_20, "../data/master_article_index_4_20.csv")

```


```{r}
  
  
totals_4_18 <- master_article_index_4_18 %>% 
  count(newspaper_state) %>% 
  rename(count = n) %>% 
  mutate(pct_whole = round(count/sum(count)*100,2)) %>% 
  arrange(desc(pct_whole)) %>% 
  mutate(rank_new = dense_rank(desc(pct_whole)))


```



Oct 29 data cleaning and updating:
master_article_index_10.19 has 7,162 articles
--contains 714 articles from proquest and howard university
--331 of the LOC articles are from the black press
--total 1,045 articles from the black press
--the 7162 is about 12% of the total corpus
--the 1045 Black press articles are about 1.7% of the total corpus

New folder: black_press_all = 1066 black press articles

```{r}
#7162 articles with the fixed URL. Includes Black Press
old_master_article_index_10.19 <- read.csv("../data/master_article_index_10.19.csv")

totals_10_19 <- old_master_article_index_10.19 %>% 
  count(newspaper_state) %>% 
  rename(count = n) %>% 
  mutate(pct_whole = round(count/sum(count)*100,2)) %>% 
  arrange(desc(pct_whole)) %>% 
  rename(pct_whole_old = pct_whole, count_old = count) %>% 
  mutate(rank_old = dense_rank(desc(pct_whole_old)))

```

#join and compare dfs

```{r}
compare <- totals_4_18 %>% 
  inner_join(totals_10_19, by="newspaper_state")

```

```{r}
# There are significant problems with the latest data
# First, there are major discrepancies with the states that were extracted.
# --Georgia, a critical state in our study, has 91 FEWER entries in the latest data
# --Pennsylvania has 215 fewer entries
# 
# The difference could be the Black press entries which weren't added.
compare %>% 
  filter(count_old > count)


```



# Full Library of Congress Newspaper List
```{r}


#Code from Khushboo Rathore
download_loc <- "../data/newspapers_list.txt"
download.file("https://chroniclingamerica.loc.gov/newspapers.txt", download_loc)

newspaper_list <- read_delim(download_loc, delim = "|")

clean_newspaper_list <- newspaper_list %>% 
  clean_names() %>% 
  select(state, title, lccn, oclc, issn, no_of_issues, first_issue_date, last_issue_date) %>% 
  rename(newspaper = title, no_issues = no_of_issues, earliest_issue = first_issue_date, latest_issue = last_issue_date) %>% 
  mutate_all(str_squish) %>% 
  mutate(earliest_issue = lubridate::mdy(earliest_issue)) %>% 
  mutate(latest_issue = lubridate::mdy(latest_issue))

#write_csv(clean_newspaper_list, "../data/newspaper_list.csv")
```

# Printing Hate Main Index of Newspapers

```{r}
#new_main_index <- read.csv("../data/mainindex_10_30.csv")
#full_list_clean <- read.csv("../data/main_index_with_names_111323.csv")
#dec_28 with cleaned names, all but 1,170 newspapers named
full_list_clean <- read.csv("../data/main_index_dec_28_2023.csv")

```


# Tolnay and Beck Lynching Inventory
```{r}

tolnay_beck <- read_csv("../data/Bailey_Beck_lynching_list_8_1_2022.csv") %>% 
  as.data.frame()

tolnay_beck <- janitor::clean_names(tolnay_beck)

```


# Main index of all extracted articles

```{r}
#12579 articles from LOC only. April 18 2024
master_article_index_4_18 <- read.csv("../data/extracted_database_index_april_16.csv") %>% 
  clean_names()


master_article_index_4_18$url_fixed <- sub("sn\\d+/\\K.*", "", master_article_index_4_18$url, perl = TRUE)
master_article_index_4_18$url_fixed  <- sub("/$", "", master_article_index_4_18$url_fixed)

#date fixed for url
master_article_index_4_18$date2 <- as.character(master_article_index_4_18$date)
master_article_index_4_18$date2 <- gsub("-", "/", master_article_index_4_18$date2)


#create sequence column
master_article_index_4_18$seq <- sub(".*/(seq-\\d+).*", "\\1", master_article_index_4_18$url)

master_article_index_4_18 <- master_article_index_4_18 %>% 
  mutate(url2 = paste(url_fixed, year, month, day, edition, seq, "0?user_id=6", sep="/"))


write.csv(master_article_index_4_18, "../data/master_article_index_4_18.csv") 

#next: compare the dates to the first index

```


```{r}

#7162 articles with the fixed URL. Includes Black Press
master_article_index_10.19 <- read.csv("../data/master_article_index_10.19.csv")

#1045 black press articles. join 714 articles + 358 LOC articles
blackindex_master <- read.csv("../data/blackindex_master.csv")

```

# Text data

```{r}


#152766 rows of text data for tokenization (6448 predominantly white press articles)
articles_oct_19 <- read.csv("../data/articles_oct_19.csv")
#Consists of this folder
lynch1 <- readtext("~/Code/hcij_lynching_phase_two/articles_10_19")

#76020 rows of BP text data for tokenization 
bp_text <- read.csv("../data/black_press_article_text_oct_19.csv")
#from this folder
bp_lynch <- readtext("~/Code/hcij_lynching_phase_two/black_press_all")

#text for just the 714 bp articles
onlybptext <- read.csv("../data/only_bp_text.csv")

```

# Geocoded articles
#Analysis
```{r}
#2783 articles all geocoded
lynch_geocoded_10.8 <- read.csv("../data/lynch_geocoded_10.8.csv")
```




```{r}
ga_lynchings <- tolnay_beck %>% 
  filter()


```