---
title: "Indexes and Lists"
author: "(redacted for peer review)"
date: "2024-06-17"
output: html_document
---

Anonymized data and code stored at OSF: https://osf.io/7kpr4/?view_only=6c106acd6cb54f6f849e8c6f9098809f



```{r include=FALSE}
#install.packages("here")
here::here()
library(tidyverse)
library(tidyr)
#install.packages("ggmap")
library(ggmap)
#register_google(key = "YOUR KEY HERE")
library(googlesheets4)
#install.packages("geosphere")
library(geosphere)
#install.packages("tigris")
#install.packages("zoo")
library(tigris)
library(stringr)
library(janitor)
library(zoo)
library(lubridate)
library(readtext)

```

# Master_article_index_6_18
June 22 data cleaning and compiling
master_article_index_6_17 has 11,223 articles
--1633 from the black press

## Load Data
```{r include=FALSE}
#metadata for 11,396 articles observed by coding team. 19% of all 60,042 entries in search
master_article_index_june_26_2024 <- read_csv("https://osf.io/download/fuh3m/?view_only=6c106acd6cb54f6f849e8c6f9098809f")


#Index of 11,223 articles of text extracted from 60,000 lynching articles: 18.7% of all 60,042 search captured
extracted_articles_index_june_22_2024 <- read_csv("https://osf.io/download/hzyw6/?view_only=6c106acd6cb54f6f849e8c6f9098809f") %>%
  as.data.frame()

#60,042 Library of Congress articles on lynching captured.
main_index <- read_csv("https://osf.io/download/hda4v/?view_only=6c106acd6cb54f6f849e8c6f9098809f")

```

### Load 11,223 extracted articles in a df
```{r include=FALSE}
#303184 rows, articles span multiple rows for tokenization
extracted_text_june_22_2024 <- read_csv("https://osf.io/download/p32he/?view_only=6c106acd6cb54f6f849e8c6f9098809f")

#subset 9589 mainstream white owned paper articles to eliminate Black newspapers
lynch1 <- lynch %>% 
    filter(black_press != "Y" | is.na(black_press))

```



```{r include=FALSE}
# 1650 from the black press
# from master_article_index_6_17 has 11,396 articles
# June 22 data cleaning and compiling

black_press_master_june_26_2024 <- master_article_index_june_26_2024 %>% 
  filter(black_press =="Y")


# black_press_master_june_26_2024 <- read_csv("#https://osf.io/download/e84j3/?view_only=6c106acd6cb54f6f849e8c6f9098809f")

black_press_extracted_text_june_22_2024 <- read_csv("https://osf.io/download/t75k2/?view_only=6c106acd6cb54f6f849e8c6f9098809f")

#write.csv(black_press_master_june_26_2024, "../data/blackindex_master_june_26_2024.csv")

bp <- black_press_master_june_26_2024 %>% 
  count(newspaper_name) %>% 
  arrange(desc(n))
#write.csv(bp, "../output_images_tables/bp_newspapers.csv")

```

# Black press index from Chronicling America
```{r}
#243 papers from the 59,967 paper search
black_papers <- read_csv("../data/black_papers.csv") %>% 
  rename(newspaper_name = Title) %>% 
  as.data.frame()

#61 separate BP titles
black_papers <- black_papers %>% 
  mutate(black = "Y")

```


### Counting the years
```{r}
years_6_26 <- master_article_index_june_26_2024 %>% 
  count(year) %>% 
  rename(count = n) %>% 
  mutate(pct_whole = round(count/sum(count)*100,2)) %>% 
  arrange(desc(pct_whole)) %>% 
  mutate(rank_new = dense_rank(desc(pct_whole)))

#write.csv(years_6_26, "../output_images_tables/years_of_news_coverage_6_26_2024.csv")

#master_article_index_10_19

old_master_article_index_10.19 <- read.csv("../data/old_article_indexes_lists/master_article_index_10.19.csv")
years_10_19 <- old_master_article_index_10.19 %>% 
  count(year) %>% 
  rename(count = n) %>% 
  mutate(pct_whole = round(count/sum(count)*100,2)) %>% 
  arrange(desc(pct_whole)) %>% 
  rename(pct_whole_old = pct_whole, count_old = count) %>%   mutate(rank_old = dense_rank(desc(pct_whole_old)))


#join and compare dfs


year_compare <- years_10_19 %>% 
  inner_join(years_6_18, by="year") %>% 
  mutate(diff = (count-count_old)) %>% 
  mutate(pct_chg = round(count-count_old)/count_old*100) %>% 
  mutate(pct_chg = round(pct_chg,2))

## fact checking years new vs old
year_compare %>% 
  filter(count_old > count)

#lost five articles in 1851, 1 in 1846. That's it
#Biggest gains in 1871, 1873, 1872, 1917, 1915, 1916

         
#NY, MA, no difference; PA, 1; DE, 6; ME, 7; SC, 8
#Biggest changes were IN, AZ, IA, CO, ID, CT, AL, A, HI, SC, AK

```



### Counting the states
```{r}
totals_6_18 <- master_article_index_june_26_2024 %>% 
  count(newspaper_state) %>% 
  rename(count = n) %>% 
  mutate(pct_whole = round(count/sum(count)*100,2)) %>% 
  arrange(desc(pct_whole)) %>% 
  mutate(rank_new = dense_rank(desc(pct_whole)))

#Il (8%), AL, IA , IN (5%), AR (4.6%), AZ, VA, OH, WI, GA top newspaper states

totals_10_19 <- old_master_article_index_10.19 %>% 
  count(newspaper_state) %>% 
  rename(count_old = n) %>% 
  mutate(pct_whole = round(count_old/sum(count_old)*100,2)) %>% 
  arrange(desc(pct_whole)) %>% 
  mutate(rank_new = dense_rank(desc(pct_whole)))

```

## join and compare dfs


```{r}
compare <- totals_6_18 %>% 
  inner_join(totals_10_19, by="newspaper_state") %>% 
  mutate(diff = (count-count_old)) %>% 
  mutate(pct_chg = round(count-count_old)/count_old*100) %>% 
  mutate(pct_chg = round(pct_chg,2))
         

#Biggest changes were AZ, IN, IA, CO, ID, AL, CT, CA, HI
#No difference; PA, WV, WY, NY, DE, SC, MA
```


### count of new pre-civil war stories

```{r}
#724 pre-civil war articles
year_compare %>% 
filter(year < "1862") %>% 
summarize(sum(count))


#69 new pre-civil war articles extracted.
year_compare %>% 
filter(year < "1862") %>% 
summarize(sum(diff))


```

# Full Library of Congress Newspaper List
```{r}


#Code from Khushboo Rathore
download_loc <- "../data/newspapers_list.txt"
download.file("https://chroniclingamerica.loc.gov/newspapers.txt", download_loc)

newspaper_list <- read_delim(download_loc, delim = "|")

clean_newspaper_list <- newspaper_list %>% 
  clean_names() %>% 
  select(state, title, lccn, oclc, issn, no_of_issues, first_issue_date, last_issue_date) %>% 
  rename(newspaper = title, no_issues = no_of_issues, earliest_issue = first_issue_date, latest_issue = last_issue_date) %>% 
  mutate_all(str_squish) %>% 
  mutate(earliest_issue = lubridate::mdy(earliest_issue)) %>% 
  mutate(latest_issue = lubridate::mdy(latest_issue))

#write_csv(clean_newspaper_list, "../data/newspaper_list.csv")
```

# Printing Hate Main Index of Newspapers

```{r}
#new_main_index <- read.csv("../data/mainindex_10_30.csv")
#full_list_clean <- read.csv("../data/main_index_with_names_111323.csv")
#dec_28 with cleaned names, all but 1,170 newspapers named
full_list_clean <- read.csv("../data/main_index_dec_28_2023.csv")

```


# Tolnay and Beck Lynching Inventory
```{r}

tolnay_beck <- read_csv("../data/Bailey_Beck_lynching_list_8_1_2022.csv") %>% 
  as.data.frame()

tolnay_beck <- janitor::clean_names(tolnay_beck)

```


