---
title: "Main Article Graphics"
author: "(redacted for peer review"
date: "2024-06-25"
output:
  word_document: default
  pdf_document: default
---

This notebook has the code for many graphics (or links to them) for "Lynching and the Press, 1805-1963."	


```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
#install.packages("sampler")
library(sampler)
#install.packages("rio")
library(rio)
#install.packages("kableExtra")
#install.packages("formattable")
library(formattable)
library(kableExtra)
library(knitr)
library(here)
```

Next, we import an index of lynching coverage -- 60,042 pages -- captured by these search terms.

# Import Data
```{r}
#metadata for 11,396 articles observed by coding team. 19% of all 60,042 entries in search
master_article_index_june_26_2024 <- read_csv("https://osf.io/download/fuh3m/?view_only=6c106acd6cb54f6f849e8c6f9098809f") %>% 
  as.data.frame()

#60,042 Library of Congress articles on lynching captured.
index <- read_csv("https://osf.io/download/hda4v/?view_only=6c106acd6cb54f6f849e8c6f9098809f")

#black press articles only
black_press_extracted_text_june_22_2024 <- read_csv("https://osf.io/download/t75k2/?view_only=6c106acd6cb54f6f849e8c6f9098809f")

```

# Sample 
A stratified random sample by year using proportional allocation.

```{r}
#sample code: ssampcalc(df, n, strata, over=0)

x <- ssampcalc(index, n=60042, strata=year, over=0.5)
x <- janitor::clean_names(x)

x$decade <- paste0(substr(x$year, 0, 3), "0")

library(kableExtra)

sample_decade <- x %>% 
  group_by(decade) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(pct_total = n/(sum(n))) %>% 
  mutate(pct_total = formattable::percent(pct_total,2)) %>% 
  rename(total = n) %>% 
  kable() %>%
  kable_styling("striped") %>%
  column_spec(1, width = ".5em") %>%
  column_spec(2, width = "1em") %>%
  column_spec(3, width = "1em") %>% 
  add_header_above(c("LOC Lynching Articles by Decade, n=60,042" = 3)) %>% 
  save_kable("../output_images_tables/sample_decade_6_26_2024.png")


#Fact check
#sum(x$nh)
#nh is the total pages per year
#wt[,1] is the percentage of the total corpus (60042 pages)
#Shows peak media coverage of lynching activity between 1893-1910
#Peak year for coverage was 1903, with 2971 pages and 4.94% of all pages


x <- ssampcalc(index, n=60042, strata=year, over=0.5)
x <- janitor::clean_names(x)
x

```

# Figure 1: Analyzing the Lynching Data

```{r}

#Here is a chart, Figure 1, that describes lynching search results by year, counting news pages with at least one lynching story in the LOC database.
count_year <- master_article_index_june_26_2024 %>% 
count(year) %>% 
   group_by(year) %>% 
#Sandwich it onto a simple ggplot
  ggplot(aes(x = year, y = n, fill = n)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
  scale_x_continuous(labels = c(seq(1800, 1960, 10)), breaks = seq(1800, 1960, 10)) +
  labs(title = "Lynching Coverage By Year, 1805-1963", 
       subtitle = "Count of Lynching Stories Examined",
       caption = "n=11,396 articles. Peak page count: 1903: 482 pages. Graphic by (redacted - peer review), 6/26/2024",
       y="Count of Pages",
       x="Year")

ggsave(here::here("../lynching_press/output_images_tables/Article_Images/Figure_1_coverage_year_6_26_2024.png"),device = "png",width=9,height=6, dpi=800)

```

Here is the list of all newspapers we captured. I'm just supplying the top 20 results.
### Total by newspaper

```{r}

#Table from Pg. 10 top 10 newspapers
total_count <- master_article_index_june_26_2024 %>%
  count() %>%
  pull(n)

newspaper <- master_article_index_june_26_2024 %>% 
  select(newspaper_name, newspaper_state) %>% 
   group_by(newspaper_name, newspaper_state) %>% 
   count(name = "n") %>% 
  mutate(pct = formattable::percent(n/total_count, 1)) %>% 
  arrange(desc(pct)) %>% 
  ungroup()


newspaper_top <- newspaper %>% 
  top_n(20,pct) %>% 
  as.data.frame()

newspaper_top

#problem with kable until I installed webshot::install_phantomjs()

#top 20 newspapers by page count
newspaper_top %>%
  kable() %>%
  kable_styling("striped") %>%
  save_kable("../output_images_tables/top_newspapers_6_26_2024.png")

```

### Total publications by state

```{r}
#total by state
state <- master_article_index_june_26_2024 %>% 
count(newspaper_state) %>% 
   group_by(newspaper_state) %>% 
  ungroup()

state <- state %>% 
  mutate(pct_total_pages =(n/sum(n))) %>% 
  arrange(desc(pct_total_pages))
         
 
state$pct_total_pages <-formattable::percent(state$pct_total_pages, 1)
state

#top states by page count
state %>%
  kable() %>%
  kable_styling("striped") %>%
  save_kable("../output_images_tables/top_states_6_26_2024.png")
```


### Regional classification for newspaper

```{r}
#Classification based on https://www.census.gov/programs-surveys/economic-census/guidance-geographies/levels.html#par_textimage_34
master_article_index_june_26_2024 <- master_article_index_june_26_2024 %>% 
  mutate(region = case_when(newspaper_state=="South Carolina" ~ "South",
                           newspaper_state=="Texas" ~ "South",
                            newspaper_state=="Louisiana" ~ "South",
                            newspaper_state=="Tennessee" ~ "South",
                            newspaper_state=="Mississippi" ~ "South",
                            newspaper_state=="Arkansas" ~ "South",
                            newspaper_state=="Alabama" ~ "South",
                            newspaper_state=="Georgia" ~ "South",
                            newspaper_state=="Virginia" ~ "South",
                            newspaper_state=="Florida" ~ "South",
                            newspaper_state=="North Carolina" ~ "South",
                            newspaper_state=="Maryland" ~ "South",
                            newspaper_state=="Delaware" ~ "South",
                            newspaper_state=="West Virginia" ~ "South",
                            newspaper_state=="Kentucky" ~ "South",
                            newspaper_state=="Missouri" ~ "Midwest",
                            newspaper_state=="Maine" ~ "Northeast",
                            newspaper_state=="New York" ~ "Northeast",
                            newspaper_state=="New Hampshire" ~ "Northeast",
                            newspaper_state=="Vermont" ~ "Northeast",
                            newspaper_state=="Massachusetts" ~ "Northeast",
                            newspaper_state=="Connecticut" ~ "Northeast",
                            newspaper_state=="Rhode Island" ~ "Northeast",
                            newspaper_state=="Pennsylvania" ~ "Northeast",
                            newspaper_state=="New Jersey" ~ "Northeast",
                            newspaper_state=="Ohio" ~ "Midwest",
                            newspaper_state=="Indiana" ~ "Midwest",
                            newspaper_state=="Kansas" ~ "Midwest",
                            newspaper_state=="Michigan" ~ "Midwest",
                             newspaper_state=="Wisconsin" ~ "Midwest",
                             newspaper_state=="Minnesota" ~ "Midwest",
                             newspaper_state=="Iowa" ~ "Midwest",
                             newspaper_state=="California" ~ "West",
                             newspaper_state=="Nevada" ~ "West",
                             newspaper_state=="Oregon" ~ "West",
                            newspaper_state=="Illinois" ~ "Midwest",
                            newspaper_state=="Nebraska" ~ "Midwest",
                            newspaper_state=="Colorado" ~ "West",
                            newspaper_state=="North Dakota" ~ "Midwest",
                            newspaper_state=="South Dakota" ~ "Midwest",
                            newspaper_state=="Montana" ~ "West",
                            newspaper_state=="Washington" ~ "West",
                            newspaper_state=="Idaho" ~ "West",
                            newspaper_state=="Wyoming" ~ "West",
                            newspaper_state=="Utah" ~ "West",
                            newspaper_state=="Oklahoma" ~ "South",
                            newspaper_state=="New Mexico" ~ "West",
                            newspaper_state=="Arizona" ~ "West",
                            newspaper_state=="Alaska" ~ "West",
                            newspaper_state=="Hawaii" ~ "West",
                            newspaper_state=="District of Columbia" ~ "South",))

```


```{r}
### Border Designation
master_article_index_june_26_2024 <- master_article_index_june_26_2024 %>% 
  mutate(border = case_when(newspaper_state=="Maryland" ~ "Border",
                            newspaper_state=="Delaware" ~ "Border",
                            newspaper_state=="West Virginia" ~ "Border",
                            newspaper_state=="Kentucky" ~ "Border",
                            newspaper_state=="Missouri" ~ "Border",
                               .default = "Not_Border"))

```


# Figure 2: State-region totals
```{r}

#total by region
region <- master_article_index_june_26_2024 %>% 
  group_by(region) %>% 
  count() %>% 
  ungroup()

region <- region %>% 
  na.omit() %>% 
  rename(total = n) 


region <- region  %>% 
   mutate(pct_total_pages = round(total/sum(total),2)) %>% 
  mutate(pct = formattable::percent(pct_total_pages,0)) %>% 
  arrange(desc(pct_total_pages))


region %>% 
  ggplot(aes(x = region, y = pct, fill = pct)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none", plot.subtitle = element_text(color = "blue", size = 8, face = "italic")) +
    scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label = scales::percent(pct_total_pages)), size = 4, hjust=.5, vjust=0) + 
  labs(title = "Regional Distribution of Lynching Coverage, 1805-1963", 
       subtitle = "Newspapers by Census Region",
       caption = "Newspapers by region with lynching coverage. n=11,396 articles. Graphic by (redacted - peer review), 6/26/2024",
       y="Pct of Pages",
       x="Region")



ggsave(here::here("../lynching_press/output_images_tables/Article_Images/Figure_2_regional_coverage_6_26_2024.png"),device = "png",width=9,height=6, dpi=800)
```



### Tolnay Beck Bailey Victim Data - Compare Trends with News Coverage

The University of Illinois holds the Tolnay_Bailey_Victim_Data of all known lynching cases from 1882-1929.

\#<https://uofi.app.box.com/s/ffmqd2rjxrdt1tvxl38d/file/110041209555>

There are 2,249 lynching cases in this database, again from 1882-1929

There is also the Tolnay, Beck & Bailey list of 5,872 cases, 1865-2020, probable and confirmed lynchings.
https://app.box.com/s/99ggc6epn4rdvritke0h/file/992017683748

**Our newspaper research reaches back much earlier than this dataset.** We have identified news reports of lynching as early as 1789.

**Below, we compare the frequency of news coverage to the Tolnay victims list.**

```{r}
tolnay_beck <- read_csv("https://osf.io/download/vb8wa/?view_only=6c106acd6cb54f6f849e8c6f9098809f") %>% 
  as.data.frame()

tolnay_beck <- janitor::clean_names(tolnay_beck)
# This contains
# tolnay_beck	5871 confirmed and probable	

```

```{r}
tolnay_beck %>% 
  count(status)

```

```{r}
tolnay_beck <- tolnay_beck %>% 
  mutate(
    status_clean = str_to_lower(status)) 
  

tolnay_beck$status_clean <- stringr::str_trim(tolnay_beck$status_clean)

tolnay_beck %>% 
  count(status_clean) 
```

```{r}
tolnay_beck <- tolnay_beck %>% 
  mutate(
    status_clean = case_when(
      status_clean == 'coincident death' ~ 'coincidental death',
      status_clean == 'possiible lynching' ~ 'possible lynching',
      TRUE ~ status_clean
    ))

install.packages('htmlTable')
library(htmlTable)

tolnay_beck$decade <- paste0(substr(tolnay_beck$year, 0, 3), "0")

tolnay_counts <- tolnay_beck %>% 
 count(status_clean) %>%
  rename(Total = n, Type = status_clean) %>% 
  mutate(Percent_Total = round(Total/5871, 3)) %>% 
  mutate(Percent_Total = formattable::percent(Percent_Total)) %>% 
  arrange(desc(Total))

tolnay_decades <- tolnay_beck %>% 
 count(decade) %>% 
  rename(Total = n) %>% 
  mutate(Percent_Total = round(Total/5871, 3)) %>% 
  mutate(Percent_Total = formattable::percent(Percent_Total)) %>% 
  arrange(desc(Total))

#install.packages("rempsyc")
library(rempsyc)

nice_table(tolnay_counts, short = TRUE)

library(kableExtra)
kbl(tolnay_counts) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "5em", background = "yellow")


tolnay_counts %>%
  # arrange(desc(n)) %>% 
 #kbl(caption = "Lynching Totals", font_size = 30) %>%
  kbl(caption = "Lynching by type, Tolnay, Beck & Bailey list of 5,872 cases, 1865-2020", font_size = 24) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>% 
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "5em", background = "yellow") 

#Tolnay Beck Lynch Totals 4_14_2023.png
 
```

```{r}
tolnay_events <- tolnay_beck %>% 
  select(year, status_clean) %>% 
group_by(year) %>% 
  count(status_clean)

tolnay_events %>% 
  pivot_wider(names_from = status_clean, values_from = n)



```
# Figure 3: Lynching Totals, Tolnay & Beck, 2022
```{r}
tolnay_beck <- tolnay_beck %>% 
  mutate(
    status_clean = case_when(
      status_clean == 'coincident death' ~ 'coincidental death',
      status_clean == 'possiible lynching' ~ 'possible lynching',
      TRUE ~ status_clean
    ))

tolnay_counts <- tolnay_beck %>% 
  count(status_clean) %>% 
  mutate(pct_total = round(n/5871, 3)) %>% 
  mutate(pct_total = formattable::percent(pct_total, 1)) 

nice_table(tolnay_counts, short = TRUE)

library(kableExtra)
kbl(tolnay_counts) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "5em", background = "yellow")


tolnay_graphic <- tolnay_counts %>%
  arrange(desc(n)) %>% 
  kbl(caption = "Lynching Totals, Tolnay & Beck, 2022", font_size = 30) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>% 
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "5em", background = "yellow") 

library(webshot)
# Save the kable table as an image
temp_html <- tempfile(fileext = ".html")
save_kable(tolnay_graphic, file = temp_html)
img_file <- tempfile(fileext = ".png")
webshot(temp_html, file = img_file, zoom = 2) # Adjust zoom to control resolution

# Convert the image to a ggplot object
img <- grid::rasterGrob(png::readPNG(img_file), interpolate = TRUE)

# Save the ggplot object as a high-resolution image
ggsave("tolnay_graphic.png", plot = ggplot() + annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf), dpi = 800, width = 10, height = 10)
```

```{r}
tolnay_beck %>% 
count(year) %>% 
   group_by(year) %>% 
#Sandwich it onto a simple ggplot
  ggplot(aes(x = year, y = n, fill = n)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
  labs(title = "Actual, Threatened Lynchings, 1865-2020", 
       subtitle = "Count of Actual, Probable Lynchings. Tolnay-Beck Data",
       caption = "n=5,871 incidents (lynchings = 5,039. Graphic by (redacted - peer review), 4/14/2023",
       y="Count",
       x="Year")
#Actual, Threatened Lynchings Tolnay 4_14_2023
```


```{r}
tolnay_beck %>% 
  select(year, status_clean) %>% 
group_by(year) %>% 
  count(status_clean) %>% 
  #Sandwich it onto a simple ggplot
  ggplot(aes(x = year, y = n, fill = n)) +
  geom_col(position = "dodge") + 
  labs(title = "Actual, Threatened Lynchings, 1865-2020", 
       subtitle = "Count of Actual, Probable Lynchings. Tolnay-Beck Data",
       caption = "n=5,871 incidents (lynchings = 5,039. Graphic by (redacted - peer review), 4/14/2023",
       y="Count",
       x="Year")

```

Year Totals - seguin_tolnay
```{r}
tolnay_beck_year <- tolnay_beck %>% 
  group_by(year) %>% 
  count(year) %>% 
  rename(total = n) %>% 
  mutate(pct_total = formattable::percent(total/5871, 3))
tolnay_beck_year
```

Year Totals - Lynching Articles
```{r}
lynching_year <- master_article_index_june_26_2024 %>% 
  group_by(year) %>% 
  count(year) %>% 
  rename(total = n) %>% 
  mutate(pct_total = formattable::percent(total/11396, 3))
lynching_year
```

We capture a stratified sample by year of the tolnay_beck victims.

It shows peak lynching activity between 1884-1895 and a significant drop off after 1922.

Our newspaper research has broadly similar findings.

# Figure 5: Ida Wells Graphic 
```{r}
combo2 <- lynching_year %>% 
  right_join(tolnay_beck_year, by="year") %>% 
  filter(year <="1963")

combo2 <- combo2 %>% 
  rename(news_total = total.x, news_pct = pct_total.x, lynch_total = total.y, lynch_pct = pct_total.y) %>% 
  mutate(gap = news_pct - lynch_pct) %>% 
  mutate(ratio = news_total/lynch_total)

# write.csv(combo2, "../output_images_tables/news_lynching_combo2_june27_2024.csv")

#plot it
pl <- ggplot(data = combo2, aes(x = year))
pl <- pl + geom_line(aes(y=lynch_pct), colour = "blue")
pl <- pl + geom_line(aes(y=news_pct), colour = "red")
pl <- pl + scale_y_continuous(labels = scales::percent)
pl <- pl + scale_x_continuous(breaks=c(1860, 1865, 1870, 1875, 1880, 1885, 1890, 1895, 1900, 1905, 1910, 1915, 1920, 1925, 1930, 1935, 1940, 1945, 1950, 1955, 1960)) 
pl <- pl + theme(axis.text.x = element_text(angle=90)) 
pl <- pl + labs(x = "Year", y = "Pct of whole")
pl <- pl + labs(title = "Newspaper Coverage vs Lynchings, 1865-1963", 
        subtitle = "Newspaper Articles (Red) vs. Actual Victims (Blue), pct of whole",
       caption = "Tolnay_Beck Victims n = 5871. Media n = 11,396 articles. Graphic by (redacted - peer review), 6/26/2024")

ggsave("../output_images_tables/Article_Images/Figure_5_ida_graph_6_26_2024.png", device = "png",width=9,height=6, dpi=800)

pl
```


```{r}
#focus on the change in 1890 - 1920
combo3 <- combo2 %>% 
  filter(year >= "1890" & year <= "1920") %>% 
  select(year, news_pct, lynch_pct)

plx <- ggplot(data = combo3, aes(x = year))
plx <- plx + geom_line(aes(y=lynch_pct), colour = "blue")
plx <- plx + geom_line(aes(y=news_pct), colour = "red")
plx <- plx + scale_x_continuous(breaks=c(1890:1920)) 
plx <- plx + scale_y_continuous(labels = scales::percent)
plx <- plx + theme(axis.text.x = element_text(angle=90)) 
plx <- plx + labs(x = "Year", y = "Pct of whole")
plx <- plx + labs(title = "Newspaper Coverage vs Lynchings, 1890-1920", 
        subtitle = "Newspaper Articles (Red) vs. Actual Victims (Blue), pct of whole",
        caption = "Tolnay_Beck Victims n = 5871. Media n = 11,396 articles. Graphic by (redacted - peer review), 6/26/2024")

ggsave("../output_images_tables/Article_Images/Figure_6_detail_ida_graph_6_26_2024.png", device = "png",width=9,height=6, dpi=800)

plx
```


### Counts of Words and Articles

```{r}
### Load 11,223 extracted articles in a df
#303184 rows, articles span multiple rows for tokenization
extracted_text_june_22_2024 <- read_csv("https://osf.io/download/p32he/?view_only=6c106acd6cb54f6f849e8c6f9098809f")

#subset 9589 mainstream white owned paper articles to eliminate Black newspapers
white_lynch <- extracted_text_june_22_2024 %>% 
    filter(black_press != "Y" | is.na(black_press))

#subset the 1634 Black press news articles
onlybptext <- extracted_text_june_22_2024 %>% 
  filter(black_press == "Y")


```

### Building lynch DF - All Stories: Count words by story
```{r}
xxx <- stringi::stri_count_words(extracted_text_june_22_2024$sentence, "\\w+") %>%
  as.data.frame() %>%
  rename(words = ".")
# 
lynch <- cbind(extracted_text_june_22_2024, xxx)
# 
y <- lynch %>% 
   select(file_id, sentence, words, year, newspaper_name, url)
# 
# # append decade information for aggregation
y$decade <- paste0(substr(y$year, 0, 3), "0")


##Average Word Count in Lynching News Coverage by decade
z <- y %>% 
  select(file_id, newspaper_name, url, words, decade) %>% 
  group_by(file_id, decade) %>% 
  summarize(total=sum(words))

mean(z$total, na.rm=TRUE)

#average words per decade and total article count
lynch_word_decade <- z %>% 
  select(decade, total) %>% 
  group_by(decade) %>% 
  summarise(
    avg_words = mean(total, na.rm = TRUE),
    num_articles = n()
  ) %>% 
  mutate(avg_words = round(avg_words, 0)) %>% 
   filter(!decade>1960)
```
# Figure 7 Avg_word_count
```{r}
lynch_word_decade %>% 
  ggplot(aes(x = decade, y = avg_words,fill = avg_words)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
  labs(title = "Average Word Count in Lynching News Coverage",
       subtitle = "Based in 11,223 extracted articles, 1805-1963",
       caption = "Graphic by (redacted - peer review), 6-25-2024",
       y="Average Article Word Count",
       x="Decade")

ggsave("../output_images_tables/Article_Images/Figure7_avg_word_count_june_25_2024.png",device = "png",width=9,height=6, dpi=800)


```


### Black press word count by decade

```{r}
b <- stringi::stri_count_words(black_press_extracted_text_june_22_2024$sentence, "\\w+") %>%
    as.data.frame() %>%
    rename(words = ".")

black_press_extracted_text_june_22_2024 <- cbind(black_press_extracted_text_june_22_2024, b)

bb <- black_press_extracted_text_june_22_2024 %>% 
   select(file_id, sentence, words, year, newspaper_name, url)
# 
# # append decade information for aggregation
bb$decade <- paste0(substr(bb$year, 0, 3), "0")

##Average Word Count in Black Press Lynching News Coverage by decade
zz <- bb %>% 
  select(file_id, newspaper_name, url, words, decade) %>% 
  group_by(file_id, decade) %>% 
  summarize(total=sum(words))

mean(zz$total, na.rm=TRUE)
#[1] 309.5641
#Average word count of Black owned newspapers was 310 words

#average words per decade and total article count
bp_lynch_word_decade <- zz %>% 
  select(decade, total) %>% 
  group_by(decade) %>% 
  summarise(
    avg_words = mean(total, na.rm = TRUE),
    num_articles = n()
  ) %>% 
  mutate(avg_words = round(avg_words, 0)) %>% 
   filter(!decade>1960)

```

### White press word count by decade

```{r}
#subset 9589 mainstream white owned paper articles to eliminate Black newspapers
white_press <- extracted_text_june_22_2024  %>% 
    filter(black_press != "Y" | is.na(black_press))

w <- stringi::stri_count_words(white_press$sentence, "\\w+") %>%
    as.data.frame() %>%
    rename(words = ".")

white_press <- cbind(white_press, w)

ww <- white_press %>% 
   select(file_id, sentence, words, year, newspaper_name, url)
# 
# # append decade information for aggregation
ww$decade <- paste0(substr(ww$year, 0, 3), "0")

##Average Word Count in white Press Lynching News Coverage by decade
www <- ww %>% 
  select(file_id, newspaper_name, url, words, decade) %>% 
  group_by(file_id, decade) %>% 
  summarize(total=sum(words))

mean(www$total, na.rm=TRUE)
#Average word count of white owned newspapers was 138 words (137.5727)

#average words per decade and total article count
w_lynch_word_decade <- www %>% 
  select(decade, total) %>% 
  group_by(decade) %>% 
  summarise(
    avg_words = mean(total, na.rm = TRUE),
    num_articles = n()
  ) %>% 
  mutate(avg_words = round(avg_words, 0)) %>% 
   filter(!decade>1960)

```


#Figure 8: Page One Analysis
Next, we count the number of articles by page number. About 27% of all lynching articles were on Page One.

```{r}
#uses the main index of 11,396 extracted articles

black_press_master_june_26_2024$decade <- paste0(substr(black_press_master_june_26_2024$year, 0, 3), "0")

bp_pageplacement <- black_press_master_june_26_2024 %>% 
  # mutate(page = str_replace(page, "seq-", "")) %>% 
  group_by(page) %>% 
  count(page) %>% 
  ungroup() %>% 
  mutate(pct =(n/sum(n))) %>% 
  mutate(pct = formattable::percent(pct, 1)) 


#bp page 1 by decade
bp_index_pages <- black_press_master_june_26_2024 %>% 
  mutate(page_one = ifelse(page > 1, FALSE, TRUE))

bp_pages_decade <- bp_index_pages %>% 
  group_by(page_one, decade) %>%
  count(page_one) %>% 
   ungroup()


bp_pages_decade2 <- bp_pages_decade %>%
  group_by(decade, page_one) %>%
  summarise(n = sum(n)) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) 


```
# Figure 9: Page 1 stories by decade


```{r}
#Using the 11,396 extracted articles, we determine the number of page 1 stories per decade. 

master_article_index_june_26_2024$decade <- paste0(substr(master_article_index_june_26_2024$year, 0, 3), "0")

x_master_article_index_june_26_2024 <- master_article_index_june_26_2024 %>% 
  select(newspaper_name, newspaper_state, sn, year, month, day, decade, edition,page, filepath)

index_pages <- x_master_article_index_june_26_2024 %>% 
  mutate(page_one = ifelse(page > 1, FALSE, TRUE))

pages_decade <- index_pages %>% 
  group_by(page_one, decade) %>%
  count(page_one) %>% 
   ungroup()


pages_decade <- pages_decade %>%
  group_by(decade, page_one) %>%
  summarise(n = sum(n)) %>%
  mutate(percentage = round(n / sum(n) * 100, 1)) 

#write.csv(pages_decade, "../output/pages_decade_6_18.csv")

pages_decade %>% 
  filter(!is.na(page_one)) %>%
  filter(decade > "1820") %>% 
  filter(decade < "1970") %>% 
  #remove outliers
  mutate(page = case_when(
    str_detect(page_one, "TRUE") ~ "PageOne",
    str_detect(page_one, "FALSE") ~ "Inside")) %>% 
  ggplot(aes(x = decade, y = percentage, fill = page)) +
  geom_col(position = "dodge") + 
  scale_fill_manual(values = c("PageOne" = "red", "Inside" = "lightblue")) + 
  labs(title = "Percentage Page One Lynching Stories, 1830-1960", 
       subtitle = "Page One Stories By Decade",
       caption = "Page 1 lynching stories peaked at 45% in the 1920s. Graphic by (redacted - peer review), 6/26/2024",
       y="Pct of Pages",
       x="Decade")


ggsave(here::here("../lynching_press/output_images_tables/Article_Images/Figure_9_pages_decade_6_26_2024.png"),device = "png",width=9,height=6, dpi=800)


```

### All pages by decade

```{r}
master_article_index_june_26_2024$decade <- paste0(substr(master_article_index_june_26_2024$year, 0, 3), "0")

count_decade <- master_article_index_june_26_2024 %>% 
  group_by(decade) %>%
  count() %>% 
    ungroup() %>% 
  mutate(pct_total = n/(sum(n))) %>% 
  mutate(pct_total = formattable::percent(pct_total,2)) %>% 
  rename(total = n) %>% 
  kable() %>%
  kable_styling("striped", full_width = F, position = "left") %>%
  column_spec(1, width = "0.001em") %>%
  column_spec(2, width = "0.001em") %>%
  column_spec(3, width = "0.001em") %>% 
  add_header_above(c("Lynching Articles by Decade, n=11,396" = 3)) %>% 
  save_kable("../output_images_tables/viewed_sample_decade_6_26_2024.png")
```



### Black Press Page One analysis

```{r}
master_article_index_june_26_2024$decade <- paste0(substr(master_article_index_june_26_2024$year, 0, 3), "0")

pageplacement <- master_article_index_june_26_2024 %>% 
  # mutate(page = str_replace(page, "seq-", "")) %>% 
  group_by(page) %>% 
  count(page) %>% 
  ungroup()

pageplacement <- pageplacement %>% 
  mutate(pct =(n/sum(n)))


pageplacement$pct <-formattable::percent(pageplacement$pct, 1)


pageplacement %>% 
  top_n(10,pct) %>% 
  mutate(page = reorder(page, -pct)) %>%
  ggplot(aes(x = page, y = pct, fill = pct)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
  #scale_x_continuous(breaks=c(1:15)) +
  scale_y_continuous(labels = scales::percent) +
  geom_text(aes(label= pct, x= page, y= pct), hjust=.5, vjust=0) +
  labs(title = "Page Placement, Lynching Coverage, 1789-1963", 
       subtitle = "Page Number Placement of Lynching Stories",
       caption = "Page 1 stories were 34% of 11,396 articles. Graphic by (redcated) , 6/26/2024",
       y="Pct of Pages",
       x="Page Number")

```



#Figure 10: Mob coverage, characterization. Click here for interactive version. https://datawrapper.dwcdn.net/fm9BS/7/
Kushboo graphic.
https://datawrapper.dwcdn.net/fm9BS/7/
https://docs.google.com/spreadsheets/d/1v6uE0owA1DLjOxOVlRs4ijFleYtH87Y-VrDOGPqNOps/edit#gid=157809296
https://docs.google.com/document/d/1QrW9yvVlTMphAVpUwk3Glh5izoaY2Q5GthwjsRcG6m4/edit

#Figure 11: Lynching Expected. (1902, July 23). Alexandria Gazette. 

#Figure 12: Newspaper, lynch mobs and justice narrative. Click here for interactive version. https://datawrapper.dwcdn.net/5zp1f/3/
https://docs.google.com/spreadsheets/d/1v6uE0owA1DLjOxOVlRs4ijFleYtH87Y-VrDOGPqNOps/edit#gid=157809296
decade_percents_Justice
https://docs.google.com/document/d/1QrW9yvVlTMphAVpUwk3Glh5izoaY2Q5GthwjsRcG6m4/edit

#Figure 13: 'Lynching as justice' least likely in Northeast newspapers.
https://datawrapper.dwcdn.net/GJ6s9/4/
https://docs.google.com/spreadsheets/d/1v6uE0owA1DLjOxOVlRs4ijFleYtH87Y-VrDOGPqNOps/edit#gid=157809296
https://docs.google.com/document/d/1QrW9yvVlTMphAVpUwk3Glh5izoaY2Q5GthwjsRcG6m4/edit

#Figure 14: Common narratives in Black press coverage of lynching
in Black Papers Topic Modeling, 3_16_2023.rmd
/Users/robwells/Code/hcij_lynching_phase_two/narratives/code/Black Papers Topic Modeling_3_16_2023.Rmd

#Figure 15 mainstrean_topics_june27.png
in Mainstream Papers topic Modeling.rmd, Line 224
/Users/robwells/Code/hcij_lynching_phase_two/narratives/code/Mainstream Papers Topic Modeling.Rmd

#Figure 16: Common two-word phrases in Black, white press by decade, 1900-1930s. Interactive graphic has details: https://infogram.com/group-3-combined-press-word-cloud-1h1749vp70lml6z. Graphic by Hannah Ziegler

#Figure 17: The Appeal, St. Paul, Minn., Oct. 15, 1904. Pg. 2


#Black Press: Count words by story
```{r}
black <- bp_text

xx <- stringi::stri_count_words(black$sentence, "\\w+") %>% 
  as.data.frame() %>% 
  rename(words = ".")

black <- cbind(black, xx)

#65257 rows only the bp files. 
onlybptext <- filter(black, grepl("bp", filename))
#write.csv(onlybptext,("../data/only_bp_text.csv"))

yy <- black %>% 
  select(filename, sentence, words, year)

# append decade information for aggregation
yy$decade <- paste0(substr(yy$year, 0, 3), "0")


zz <- yy %>% 
  select(filename, words, decade) %>% 
  group_by(filename, decade) %>% 
  summarize(total=sum(words))

#Count words by decade
black_word_decade <- zz %>% 
  select(decade, total) %>% 
  group_by(decade) %>% 
    summarise(
    avg_words = mean(total, na.rm = TRUE),
    num_articles = n() )%>% 
  mutate(avg_words = round(avg_words, 0)) 

library(kableExtra)
# black_articles_decade %>%
  black_word_decade %>%
  kbl(caption = "Black Press Article Totals", font_size = 30) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>% 
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "5em", background = "yellow") 

#1045 black press articles. join 714 articles + 358 LOC articles
blackindex_master <- read.csv("../data/blackindex_master.csv")

#Count articles by year
black_articles <- blackindex_master %>% 
  select(filename, year) %>% 
  group_by(year) %>%
  count()


black_articles_decade <- zz %>% 
  select(decade, filename) %>% 
  group_by(decade) %>%
  count() %>% 
  mutate(Pct_Total =formattable::percent(round(n/1045,2)))

library(kableExtra)
black_articles_decade %>%
  kbl(caption = "Black Press Article Totals", font_size = 30) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>% 
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "5em", background = "yellow") 

```

# BP word count by decade
```{r}
black_word_decade %>% 
  ggplot(aes(x = decade, y = avg_words,fill = avg_words)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
  labs(title = "Black Press Avg Word Count in Lynching News Coverage",
       subtitle = "Based in 1,045 extracted articles, 1892-2002",
       caption = "Graphic by (redacted - peer review), 12-26-2023",
       y="Average Article Word Count",
       x="Decade")

#ggsave("../output_images_tables/FigureX_black_press_avg_word_count_ap_19.png",device = "png",width=9,height=6, dpi=800)


```





    --30--
