---
title: "Main Index"
author: "Khushboo Rathore"
date: "2023-11-01"
output: html_document
---
# CLEAN MAIN INDEX
```{r}
main_index <- read_csv("../hcij_lynching_phase_two/Storage_Older_Versions/mainindex.csv")
```

## Cleaning lists
```{r}
alabama <- c("Ala")
alaska <- c("Alas", "Alask")
arizona <- c("Ari", "Ariz", "ArizT", "ATA", "Cochise", "Marico", "Pima", "PimaCo", "Pin")
arkansas <- c("A", "Ark", "Arkcurrent", "Faulkne", "Ar")
california <- c("Butte", "Ca", "Cal", "Calif", "El", "ElDora", "Placer", "Cali")
colorado <- c("Ba", "Col", "Colo", "Conejo", "DeltaCo", "Elbert", "Logan", "Montez", "RubyCaGunnisonCountyColo", "Wel", "WeldCou")
connecticut <- c("Con", "Conn", "Litc")
delaware <- c("De", "Del")
florida <- c("F", "Fl", "Fla", "MarionC")
georgia <- c("Ga")
hawaii <- c("Hawai", "HawaiianIsland", "HI", "Maui", "TH")
idaho <- c("Id", "Ida", "Idah", "Idaho", "North")
illinois <- c("Il", "Ill")
indiana <- c("Ia", "IAi", "Ind", "MarshallCountyInd", "Ran", "Wayne")
iowa <- c("Audubo", "CedarC", "How", "Howard", "Io", "Iow", "Maha", "TamaCo", "Winnes", "I")
kansas <- c("AllenCou", "K", "Ka", "Kan", "Kansa", "Sum")
kentucky <- c("Bourbon", "Ky", "Madis", "Wo")
louisiana <- c("Attak", "Bossi", "Calcasie", "GrantP", "L", "La", "Lna", "P", "Par", "Pari")
maine <- c("Me")
maryland <- c("Md")
massachusetts <- c()
michigan <- c("Mic", "Mich", "StClair", "LSM")
minnesota <- c("Be", "Beltra", "BlueE", "Brown", "Goodh", "Min", "Minn", "MT", "PineCou", "Stevens", "StL", "St")
mississippi <- c("Cop", "DeSot", "Lafayet", "Lefl", "MT", "Marshal", "Mis", "Miss", "Stone")
missouri <- c("Ada", "Audrain", "Ch", "IronC", "Lafa", "Missour", "Mo", "RayC", "Salin", "ScottC")
montana <- c("MTM", "Mont", "Montcurrent", "Mon")
nebraska <- c("BoxB", "Cher", "H","Neb", "Nebr", "Nebra", "Nebras", "Nebrask", "Nem", "Webs")
nevada <- c("Nev", "NT")
new_hampshire <- c()
new_jersey <- c("NJ")
new_mexico <- c("Gu", "MoraCo", "NM", "NMT", "Rooseve", "Socorr", "Torra")
new_york <- c("NY")
north_carolina <- c("E", "Edge", "Meck", "NC", "Watauga")
north_dakota <- c("Billings", "Bott", "D", "DickeyC", "DT", "Gr", "McLea", "ND", "Richl", "Stark", "Star", "Stut", "Ward", "WardCou", "Will")
ohio <- c("Ashlan", "Bro", "Hancoc", "High", "Ho", "HolmesCoOOhio", "Mahon", "Meigs", "O", "Oh", "Ohi", "OO", "OOh", "OOhi", "OOhio", "Sandus", "StarkC", "Vinto", "Woo")
oklahoma <- c("Choctaw", "CraigC", "Indi", "India", "Indian", "IndianT", "IndTe", "Okla", "Oklah", "OTO")
oregon <- c("Lin", "Lincoln", "LinnCo", "Morrow", "Or", "Orego", "Wal")
pennsylvania <- c("Pa")
rhode_island <- c()
south_carolina <- c("Claren", "SC")
south_dakota <- c("Bl", "Broo", "Brule", "Dako", "S", "DayCo", "DTS", "Haakon", "HandCo", "Pen", "Rober", "SD", "South", "Stanley", "Unio")
tennessee <- c("GibsonC", "Hardem", "McNairy", "MorganC", "T", "Te", "Ten", "Tenn")
texas <- c("Tex")
utah <- c("CityUt", "U", "Uta")
vermont <- c("St. Johnsb", "Orlean", "Vt")
virginia <- c("Augus", "Highl", "V", "Va")
washington <- c("Cheha", "OT", "Wa", "Wash", "Washin", "WT", "Was")
w_dc <- c("DC")
west_virginia <- c("VaW", "WV", "WVa", "W")
wisconsin <- c("Ashland", "Jeff", "Pi", "Rusk", "Vi", "Wi", "Wis")
wyoming <- c("Carbo", "Wyo")

```

## Clean given states
```{r}
# main_index <- read_csv("../data/mainindex.csv")

x <- main_index %>% 
  count(newspaper_state) %>% 
  arrange(desc(n))

clean_main_index <- main_index %>% 
  # Clean out any numbers
  mutate(newspaper_state_clean = str_squish(gsub("[0-9]", "", newspaper_state))) %>% 
  # Clean out any non-letter characters
  mutate(newspaper_state_clean = str_squish(gsub("\\W", "", newspaper_state_clean))) %>% 
  mutate(newspaper_state_clean = case_when(
    newspaper_state_clean %in% alabama ~ "AL",
    newspaper_state_clean %in% alaska ~ "AK",
    newspaper_state_clean %in% arizona ~ "AZ",
    newspaper_state_clean %in% arkansas ~ "AR",
    newspaper_state_clean %in% california | str_detect(newspaper_city, "Grass Valley") ~ "CA",
    newspaper_state_clean %in% colorado | str_detect(newspaper_city, "Cañon City") ~ "CO",
    newspaper_state_clean %in% connecticut | str_detect(newspaper_city, "New Britain") ~ "CT",
    newspaper_state_clean %in% delaware ~ "DE",
    newspaper_state_clean %in% w_dc ~ "DC",
    newspaper_state_clean %in% florida ~ "FL",
    newspaper_state_clean %in% georgia ~ "GA",
    newspaper_state_clean %in% hawaii ~ "HI",
    newspaper_state_clean %in% idaho | (newspaper_state_clean == "I" & str_detect(newspaper_city, "Silver City")) ~ "ID",
    newspaper_state_clean %in% illinois ~ "IL",
    newspaper_state_clean %in% indiana | str_detect(newspaper_city, "Bloomington|Indianapolis") ~ "IN",
    newspaper_state_clean %in% iowa | str_detect(newspaper_city, "Mashalltown|Independence")~ "IA",
    newspaper_state_clean %in% kansas ~ "KS",
    newspaper_state_clean %in% kentucky ~ "KY",
    newspaper_state_clean %in% louisiana ~ "LA",
    newspaper_state_clean %in% maine ~ "ME",
    newspaper_state_clean %in% maryland | str_detect(newspaper_city, "Port Tobacco|Leonard Town") ~ "MD",
    newspaper_state_clean %in% michigan | (newspaper_state_clean == "M" & str_detect(newspaper_city, "Grand Rapids")) | str_detect(newspaper_city, "East Saginaw|Constantine|Grand Haven") ~ "MI",
    newspaper_state_clean %in% montana | str_detect(newspaper_city, "Stevensville|Diamond City|Philipsburg|Great Falls|Fort Benton") ~ "MT",
    newspaper_state_clean %in% missouri | str_detect(newspaper_city, "Farmington") ~ "MO",
    newspaper_state_clean %in% minnesota | str_detect(newspaper_city, "Grand Marais|Little Falls|Fergus Falls|Sauk Rapids|Minneapolis|White Earth|Worthington") ~ "MN",
    newspaper_state_clean %in% mississippi | (newspaper_state_clean == "M" & str_detect(newspaper_city, "Philadelphia|Water Valley")) | (newspaper_state_clean == "Mi" & str_detect(newspaper_city, "Hattiesburg|Leakesville|Poplarville|Port Gibson")) ~ "MS",
    newspaper_state_clean %in% nebraska | str_detect(newspaper_city, "North Platte|Grand Island|Nemaha City|Dakota City") ~ "NE",
    newspaper_state_clean %in% nevada | (newspaper_state_clean == "Ne" & str_detect(newspaper_city, "Silver City")) | str_detect(newspaper_city, "Carson City|Gardnerville") ~ "NV",
    newspaper_state_clean %in% new_jersey | str_detect(newspaper_city, "Mount Holly|Perth Amboy|Penn's Grove") ~ "NJ",
    newspaper_state_clean %in% new_mexico | str_detect(newspaper_city, "Silver City|Albuquerque") ~ "NM",
    newspaper_state_clean %in% new_york ~ "NY",
    newspaper_state_clean %in% north_carolina | (newspaper_state_clean == "N" & str_detect(newspaper_city, "Hillsborough")) | str_detect(newspaper_city, "Jacksonville|Chapel Hill") ~ "NC",
    newspaper_state_clean %in% north_dakota | str_detect(newspaper_city, "Bismarck|Pembina|Valley City|Grand Forks") ~ "ND",
    newspaper_state_clean %in% oregon | str_detect(newspaper_city, "Pendleton") ~ "OR",
    newspaper_state_clean %in% ohio ~ "OH",
    newspaper_state_clean %in% oklahoma ~ "OK",
    newspaper_state_clean %in% pennsylvania ~ "PA",
    newspaper_state_clean %in% south_carolina ~ "SC",
    newspaper_state_clean %in% wisconsin ~ "WI",
    newspaper_state_clean %in% south_dakota | str_detect(newspaper_city, "Gann Valley|Mitchell|Hurley|Miller") ~ "SD",
    newspaper_state_clean %in% texas | str_detect(newspaper_city, "Brownsville|San Antonio") ~ "TX",
    newspaper_state_clean %in% tennessee ~ "TN",
    newspaper_state_clean %in% utah ~ "UT",
    newspaper_state_clean %in% vermont ~ "VT",
    newspaper_state_clean %in% washington | str_detect(newspaper_city, "North Yakima|White Bluffs") ~ "WA",
    newspaper_state_clean %in% west_virginia | str_detect(newspaper_city, "Charles|Clarksburg|Lewisburg|Wheeling|Morgantown") ~ "WV",
    newspaper_state_clean %in% virginia ~ "VA",
    newspaper_state_clean %in% wisconsin ~ "WI",
    newspaper_state_clean %in% wyoming ~ "WY",
    TRUE ~ newspaper_state_clean
  ))

y <- clean_main_index %>% 
  count(newspaper_state_clean) %>% 
  arrange(desc(n))

#347 categories in the newspaper_states, needs to be cleaned to 50 or so categories in standard two-digit state format, ie. GA for Georgia, CA for California

write.csv(clean_main_index,"../data/mainindex_10_25.csv")

```

## Filters for ga, ms, na titles
```{r}
ga_papers <- clean_main_index %>% 
  filter(newspaper_state_clean =="GA") %>% 
  group_by(newspaper_state_clean, newspaper_name) %>% 
  count()

#write.csv(ga_papers,"../output/ga_papers.csv")

ga_papers_years <- clean_main_index %>% 
  filter(newspaper_state_clean =="GA") %>% 
  group_by(newspaper_state_clean, newspaper_name, year) %>% 
  count()

#write.csv(ga_papers_years,"../output/ga_papers_years.csv")


ms_papers <- clean_main_index %>% 
  filter(newspaper_state_clean =="MS") %>% 
  group_by(newspaper_state_clean, newspaper_name) %>% 
  count()

#write.csv(ms_papers,"../output/ms_papers.csv")

ms_papers_years <- clean_main_index %>% 
  filter(newspaper_state_clean =="MS") %>% 
  group_by(newspaper_state_clean, newspaper_name, year) %>% 
  count()

#write.csv(ms_papers_years,"../output/ms_papers_years.csv")


#isolate the NAs
df_na <- clean_main_index %>% filter(if_all(c(newspaper_state_clean), ~ is.na(.)))


df_na %>% 
    count(newspaper_city) %>% 
  arrange(desc(n))


```


## Clean NAs
```{r}
new_main_index <- read_csv("../data/mainindex_10_25.csv")

clean_main_index <- new_main_index %>% 
  mutate(newspaper_state_clean = case_when(
    str_detect(newspaper_city, "San Francisco|Los Angeles|Sacramento") ~ "CA",
    str_detect(newspaper_city, "Salt Lake City|Great Salt Lake") ~ "UT",
    str_detect(newspaper_city, "Washington") ~ "DC",
    str_detect(newspaper_city, "York") ~ "NY",
    str_detect(newspaper_city, "Richmond|Lynchburg") ~ "VA",
    str_detect(newspaper_city, "Grand Rapids") ~ "MI",
    str_detect(newspaper_city, "Mineral Point") ~ "WI",
    str_detect(newspaper_city, "Honolulu") ~ "HI",
    str_detect(newspaper_city, "Omaha") ~ "NE",
    str_detect(newspaper_city, "Shepherdstown") ~ "WV",
    str_detect(newspaper_city, "Ste. Genevieve") ~ "MO",
    str_detect(newspaper_city, "Maysville") ~ "KY",
    str_detect(newspaper_city, "Savannah") ~ "GA",
    str_detect(newspaper_city, "Winston|Hendersonville") ~ "NC",
    str_detect(newspaper_city, "West Randolph|St. Johnsbury") ~ "VT",
    str_detect(newspaper_city, "Redwood Falls") ~ "MN",
    str_detect(newspaper_city, "St. Clairsville|Hillsborough") ~ "OH",
    str_detect(newspaper_city, "Waterbury|New Haven") ~ "CT",
    str_detect(newspaper_city, "Medicine Lodge|Baxter Springs") ~ "KS",
    str_detect(newspaper_city, "Donaldsonville|New Orleans") ~ "LA",
    str_detect(newspaper_name, "Le Meschacébé|The weekly messenger") ~ "LA",
    TRUE ~ newspaper_state_clean
  ))

filtered_main_index <- clean_main_index %>% 
  filter(is.na(newspaper_state_clean)) %>% 
  filter(!is.na(newspaper_city))
  

cities_list <- filtered_main_index %>% 
  group_by(newspaper_city) %>% 
  count()

no_city <- clean_main_index %>% 
  filter(is.na(newspaper_state_clean)) %>% 
  filter(is.na(newspaper_city))

no_city %>% 
  count(newspaper_state)

write.csv(new_main_index,"../data/mainindex_10_30.csv")

```


```{r}
ga_papers <- new_main_index %>% 
  filter(newspaper_state_clean =="GA") %>% 
  group_by(newspaper_state_clean, newspaper_name) %>% 
  count()
sum(ga_papers$n)
#997

ga_papers1 <- clean_main_index %>% 
  filter(newspaper_state_clean =="GA") %>% 
  group_by(newspaper_state_clean, newspaper_name) %>% 
  count()
sum(ga_papers1$n)
#1085

#write.csv(ga_papers,"../output/ga_papers.csv")

ga_papers_years <- new_main_index %>% 
  filter(newspaper_state_clean =="GA") %>% 
  group_by(newspaper_state_clean, newspaper_name, year) %>% 
  count()

#write.csv(ga_papers_years,"../output/ga_papers_years.csv")


ms_papers <- new_main_index %>% 
  filter(newspaper_state_clean =="MS") %>% 
  group_by(newspaper_state_clean, newspaper_name) %>% 
  count()
#sum(ms_papers$n)
#1084

ms_papers1 <- clean_main_index %>% 
  filter(newspaper_state_clean =="MS") %>% 
  group_by(newspaper_state_clean, newspaper_name) %>% 
  count()
#sum(ms_papers1$n)
#1084

#write.csv(ms_papers,"../output/ms_papers.csv")

ms_papers_years <- new_main_index %>% 
  filter(newspaper_state_clean =="MS") %>% 
  group_by(newspaper_state_clean, newspaper_name, year) %>% 
  count()

```



#Notes 
Alabama: "Ala
Alaska: "Alas", "Alask
Arizona: "Ari", "Ariz", "ArizT", "ATA", "Cochise", "Marico", "Pima", "PimaCo", "Pin
Arkansas: "A", "Ark", "Arkcurrent", "Faulkne
California: "Butte", "Ca", "Cal", "C & Grass Valley", "Calif", "El", "ElDora", "Placer", "Cali"
Colorado: "Ba", "Co & Cañon City", "Col", "Colo", "Conejo", "DeltaCo", "Elbert", "Logan", "Montez", "RubyCaGunnisonCountyColo", "Wel", "WeldCou
Connecticut: "Co & New Britain", "Con", "Conn", "Litc
Delaware: "De", "Del", "
Florida: "F", "Fl", "Fla", "MarionC
Georgia: "Ga
Hawaii: "Hawai", "HawaiianIsland", "HI", "Maui", "TH
Idaho: "I & Silver City", "Id", "Ida", "Idah", "Idaho", "North
Illinois: "Il", "Ill
Indiana: "I & Bloomington", "I & Indianapolis", "Ia", "Iai", "Ind", "MarshallCountyInd", "Ran", "Wayne
Iowa: "Audubo", "CedarC", "How", "Howard", "I & Marshalltown", "I & Independence", "Io", "Iow", "Maha", "TamaCo", "Winnes
Kansas: "Allen Cou", "K", "Ka", "Kan", "Kansa", "Sum"
Kentucky: "Bourbon", "Ky," "Madis", "Wo
Louisiana: "Attak", "Bossi", "Calcasie", "GrantP", "L", "La", "Lna", "P", "Par", "Pari
Maine: "Me
Maryland: "M & Port Tobacco", "M & Leonard Town", "Md
Massachusetts
Michigan: "LSM", "M & Grand Rapids", "M & East Saginaw", "Mic", "Mich", "StClair", "Constantine & Mi", "Grand Haven & Mi"
Minnesota: "Be", "Beltra", "BlueE", "Brown", "C & Grand Marais", "Goodh", "M & Little Falls", "M & Fergus Falls", "M & Grand Marais", "M & Sauk Rapids", "Min", "Minn", "MT", "PineCou", "St (Excepting Missouri)", "Stevens", "StL", "Minneapolis & Mi", "White Earth & Mi", "Worthington & Mi
Mississippi: "Cop", "DeSot", "Lafayet", "Lefl", "M & Water Valley", "M & Philadelphia", "MT", "Marshal", "Mis", "Miss", "Stone", "Hattiesburg & Mi", "Leakesville & Mi", "Poplarville & Mi", "Port Gibson & Mi
Missouri: "Ada", "Audrain", "Ch", "IronC", "Lafa", "Missour", "Mo (excepting Montana examples)", "RayC", "Salin", "ScottC", "Farmington & St"
Montana: "M & Stevensville", "M & Diamond City", "MTM", "Philipsburg & Mo", "Mo & Great Falls", "Mo & Fort Benton", "Mont", "Montcurrent", "MTM", "Mon"
Nebraska: "BoxB", "Cher", "H", "N & North Platte", "N & Grand Island", "Ne & Nemaha City", "Ne & Dakota City", "Neb", "Nebr", "Nebra", Nebras", "Nebrask", "Nem", "Webs
Nevada: "Ne & Carson City", "Ne & Silver City", "Nev", "NT
New Hampshire
New Jersey: "Bu & Mount Holly", "N & Perth Amboy", "NJ", "Penn's Grove & S
New Mexico: "Gu", "MoraCo", "N & Silver City", "N & Albuquerque", "Ne & Albuquerque", "NM", "NMT", "Rooseve", "Socorr", "Torra
New York: "NY
North Carolina: "E", "Edge", "Meck", "N & Jacksonville", "N & Hillsborough", "N & Chapel Hill", "NC", "Watauga
North Dakota: "Billings", "Bott", "D", "Dakot & Bismarck", "Dakota & Pembina", 'Star", "DickeyC", "DT", "Gr", "McLea", "N & Valley City", "N & Grand Forks", "ND", "Richl", "Stark", "Stut", "Ward", "WardCou", "Will
Ohio: "Ashlan", "Bro", "Hancoc", "High", "Ho", "HolmesCoOOhio", "Mahon", "Meigs", "O (Excepting Oregon)", "Oh", "Ohi", "OO", "OOh", "OOhi", "OOhio", "Sandus", "StarkC", "Vinto", "Woo
Oklahoma: "Choctaw", "CraigC", "Indi", "India", "Indian", "IndianT", "IndTe", "Okla", "Oklah", "OTO
Oregon: "Lin", "Lincoln", "LinnCo", "Morrow", "O & Pendleton", "Or", "Orego", "Wal
Pennsylvania: "Pa
Rhode Island
South Carolina: "Claren", "SC
South Dakota: "Bl", "Broo", "Brule", "Gann Valley & Dakota", "Dako", "Dakot & Mitchell", "S (Excepting NJ)", "Dakota & Hurley", "Dakota & Miller", "DayCo", "DTS", "Haakon", "HandCo", "Pen", "Rober", "SD", "South", "Stanley", "Unio
Tennessee: "GibsonC", "Hardem", "McNairy", "MorganC", "T", "Te (excepting Texas results)", "Ten", "Tenn
Texas: "Brownsville & Te", "San Antonio & Te", "Tex
Utah: "CityUt", "U", "Uta
Vermont: "St. Johnsb", "Orlean", "Vt
Virginia: "Augus", "Highl", "V (Excepting WV)
Washington: "Cheha", "OT", "North Yakima & W", "White Bluffs & W", "Wa", "Wash", "Washin", "WT", "Port Townsend", "Was"
Washington D.C.: "DC
West Virginia: "Charles Town & V", "Charlestown & Va", "Clarksburg & Va", "Lewisburg & Va", "Morgantown & Va", "Wheeling & Va", W, "VaW", "WV", "WVa
Wisconsin: "Ashland", "Jeff", "Pi", "Rusk", "Vi", "Wi", "Wis
Wyoming: "Carbo", "Wyo
