---
title: "Mob Analysis"
author: "Rob Wells"
date: "2023-11-15"
output: html_document
---
```{r message=FALSE, warning=FALSE}
#install.packages("here")
here::here()
library(tidyverse)
library(tidyr)
#install.packages("ggmap")
library(ggmap)
#register_google(key = "XXXX")
library(googlesheets4)
library(googledrive)
#install.packages("geosphere")
library(geosphere)
#install.packages("janitor")
library(stringr)
```

```{r}

googledrive::drive_auth()
# 
googlesheets4::gs4_deauth()

#mob <- read_sheet("https://docs.google.com/spreadsheets/d/1oKkRSInN8tO6Z-kyMoIUYOX1uHQhP7FdrR1xie4O-XQ/edit?usp=sharing")

#updates with Rachel McCrea's corrections
mob <- read_sheet("https://docs.google.com/spreadsheets/d/1-zwBtcpdH1Hnb5WROJVuPdm_HC9nTmDl-dbiSHE5tJ8/edit#gid=10206338")
```


```{r}

mob <- mob %>% 
  janitor::clean_names() 

#strip commas
mob <- mob %>% 
  mutate(code = str_replace_all(code, ","," ")) 

#new column, assign a 1 for any instance per row
mob <- mob %>%
  mutate(
    hostile = ifelse(grepl("\\bHostile\\b", code), 1, 0),
    neutral = ifelse(grepl("\\bNeutral\\b", code), 1, 0),
    orderly = ifelse(grepl("\\bOrderly\\b", code), 1, 0),
    justice = ifelse(grepl("\\bJustice\\b", code), 1, 0),
    identified = ifelse(grepl("\\bIdentified\\b", code), 1, 0),
    unsure = ifelse(grepl("\\bUnsure\\b", code), 1, 0),
    other = ifelse(grepl("\\bOther\\b", code), 1, 0)
  )
```

### Counting progress
```{r}
mob %>% 
  count(your_name) %>% 
  arrange(your_name)



```



#add decade, year
```{r}
mob <- mob %>% 
  mutate(date1 = lubridate::ymd(date)) %>% 
  mutate(year = lubridate::year(date1))



mob <- mob %>% 
    mutate(decade = case_when(
      year < 1800 ~ "pre1800",
      year >= 1800 & year <=1809 ~ "1800s",
      year >= 1810 & year <=1819 ~ "1810s",
      year >= 1820 & year <=1829 ~ "1820s",
      year >= 1830 & year <=1839 ~ "1830s",
      year >= 1840 & year <=1849 ~ "1840s",
      year >= 1850 & year <=1859 ~ "1850s",
      year >= 1860 & year <=1869 ~ "1860s",
      year >= 1870 & year <=1879 ~ "1870s",
      year >= 1880 & year <=1889 ~ "1880s",
      year >= 1890 & year <=1899 ~ "1890s",
      year >= 1900 & year <=1909 ~ "1900s",
      year >= 1910 & year <=1919 ~ "1910s",
      year >= 1920 & year <=1929 ~ "1920s",
      year >= 1930 & year <=1939 ~ "1930s",
      year >= 1940 & year <=1949 ~ "1940s",
      year >= 1950 & year <=1959 ~ "1950s",
      year >= 1960 & year <=1969 ~ "1960s",
      year >= 1970 ~ "post1970s"
         ))

```



```{r}
lynch_geocoded_10.8 <- read.csv("../data/lynch_geocoded_10.8.csv")


mob1 <- mob %>% 
  select(docname, newspaper, date, url, hostile, neutral, orderly, justice, identified, unsure, other) %>% 
  as.data.frame()

mob2 <- mob1 %>% 
  left_join(lynch_geocoded_10.8, by=c("docname"="file_id", "url"))

write.csv(mob2, "../output/mob_full_11_15.csv")
/Users/robwells/Code/Jour389L/output
write.csv(mob2, "/Users/robwells/Code/Jour389L/output/mob_full_11_15.csv")
```

# Oct 19 2024 - cleaned 30 BP articles from the Nov 2023 coding

```{r}

mob2 <- read_csv("/Users/robwells/Code/Jour389L/output/mob_full_11_15.csv")

#Nov 2023 index - 7162 articles with 331 black press.
nov_2023_index <- read_csv("/Users/robwells/Code/Jour389L/data/master_article_index_10.19.csv")

nov_2023_index <- nov_2023_index |> 
  mutate(black_press = str_squish(black_press)) |>
  mutate(black_press = case_when(
    black_press != "Y" | is.na(black_press) ~ "N",
    black_press=="Y" ~ "Y",
    TRUE ~ black_press
  )) 

nov_2023_index |> 
  count(black_press)


wp_bp_index <- nov_2023_index |> 
  select(file_id2, newspaper_name, date, black_press, filename,sn)

#14 black press publications in the Nov 2023 mob categorization data
new_mob3 <- mob2 |> 
  inner_join(wp_bp_index, by=c("sn")) |> 
  filter(black_press =="Y") |> 
  distinct(sn)

#remove black press. now 3147 articles. cut 30 articles
mob_cleaned <- mob2 |> 
  anti_join(new_mob3, by=("sn"))

mob_cleaned <- mob_cleaned |> 
  mutate(year = year(date.x),
         decade = paste0(substr(year, 0, 3), "0")
         )


mob_cleaned <- mob_cleaned[ -c(1) ]

write.csv(mob_cleaned, "/Users/robwells/Code/lynching_press/output_images_tables/mob_cleaned_10_20_2024.csv")
```


#New calculations without BP
#oct 20 2024
```{r}

mob_cleaned <- read_csv("../output_images_tables/mob_cleaned_10_20_2024.csv")

mob_summary <- mob_cleaned %>% 
  group_by(decade) %>% 
  summarize(
    total_hostile = sum(hostile, na.rm = TRUE),
    total_neutral = sum(neutral, na.rm = TRUE),
    total_orderly = sum(orderly, na.rm = TRUE),
    total_justice = sum(justice, na.rm = TRUE),
    total_identified = sum(identified, na.rm = TRUE),
    total_unsure = sum(unsure, na.rm = TRUE),
    grand_total = n() 
    ) %>% 
        mutate(
    percent_hostile = round(total_hostile / grand_total * 100),
    percent_neutral = round(total_neutral / grand_total * 100),
    percent_orderly = round(total_orderly / grand_total * 100),
    percent_justice = round(total_justice / grand_total * 100),
    percent_identified = round(total_identified / grand_total * 100),
    percent_unsure = round(total_unsure / grand_total * 100)
  )

write.csv(mob_summary, "/Users/robwells/Code/lynching_press/output_images_tables/mob_summary_10_20_2024.csv")

```


```{r}

# Reshape the data to long format
mob_long <- mob_summary %>%
  select(decade,percent_hostile,percent_orderly, percent_neutral) |> 
  filter(decade > 1820) |> 
  pivot_longer(
    cols = starts_with("percent_"), 
    names_to = "story_type", 
    values_to = "percentage"
  ) 

# Plot with side-by-side bars
mob_long %>%
  ggplot(aes(x = factor(decade), y = percentage, fill = story_type)) +
  geom_col(position = "dodge", stat = "identity") +
    geom_text(
    data = subset(mob_long, story_type == "percent_neutral"),  # Filter only neutral bars
    aes(label = paste0(percentage, "%")), 
 #   position = position_dodge(width = 0.5),  # Align with bars
 #   vjust = -0.1,
   hjust = -.3,# Slightly above the bar
    angle = 90      # Rotate the text 90 degrees
  ) +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  scale_fill_manual(
    values = c("percent_hostile" = "red", 
               "percent_neutral" = "blue",
                "percent_orderly" = "#458B00"),
    labels = c("Hostile", "Neutral", "Orderly")
  ) +
  labs(
    title = "Lynch mobs often portrayed neutrally in white newspapers",
    subtitle = "Percent of white newspaper coverage portrayals of lynch mobs",
    caption = "1800s removed, lack of data. n=3,147 articles. Graphic by (redacted - peer review), 10/20/2024",
    y = "Pct of Pages",
    x = "Decade",
    fill = "Story Type"
  ) 


ggsave(here::here("../lynching_press/output_images_tables/Article_Images/Figure_11_mob_coverage_10_20_2024.png"),device = "png",width=9,height=6, dpi=800)

```

#Figure 13: Newspaper, lynch mobs and justice narrative. 
#Fixed 10-20-2024

```{r}

# Reshape the data to long format
justice <- mob_summary %>%
  select(decade,percent_justice) |> 
  filter(decade > 1820) |> 
  pivot_longer(
    cols = starts_with("percent_"), 
    names_to = "story_type", 
    values_to = "percentage"
  ) 

# Plot with side-by-side bars
justice %>%
  ggplot(aes(x = factor(decade), y = percentage, fill = percentage)) +
  geom_col(position = "dodge", stat = "identity") +
    geom_text(
    data = subset(justice, story_type == "percent_justice"),  
    aes(label = paste0(percentage, "%")), 
 #   position = position_dodge(width = 0.5),  # Align with bars
    vjust = -0.1,
   hjust = .5,# Slightly above the bar
    #angle = 90      # Rotate the text 90 degrees
  ) +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  theme(legend.position = "none") +
  labs(
    title = "Lynching as 'justice' drops after 1830s in white newspapers",
    subtitle = "Predominantly white news coverage equating lynch mobs with justice",
    caption = "1800s removed, lack of data. n=3,147 articles. Graphic by (redacted - peer review), 10/20/2024",
    y = "Pct of Pages",
    x = "Decade") 


ggsave(here::here("../lynching_press/output_images_tables/Article_Images/Figure_13_mob_justice_10_20_2024.png"),device = "png",width=9,height=6, dpi=800)

```


# Create the plot
ggplot(mob_melt, aes(x = decade, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Decade", y = "Percentage", fill = "Variable") +
  theme_minimal()
  

# mob2 <- mob2 %>% 
#   select(docname, newspaper_name, date.x, url, hostile, neutral, orderly, justice, identified, unsure, other, lynch_address, newspaper_state_code, year, city_lynch, state_lynch, miles, decade, Newspaper_Region, total_words)



```


